---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# camcorderplus

<!-- badges: start -->
<!-- badges: end -->

The goal of camcorderplus is to provide an extension to the functionality of {camcorder} by Ellis Hughes (doi:10.32614/CRAN.package.camcorder).

NOTE: Accessing internal camcorder:::get_file_records().
Used because there's no exported equivalent at the time of writing (2025-06).
May break if camcorder changes internal API.


## Installation

You can install the development version of camcorderplus like so:

```{undefined eval=FALSE, include=TRUE}
# install.packages("remotes")
remotes::install_github("yourusername/camcorderplus")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r include=FALSE}
unlink(file.path(tempdir(), "gg_history_export"), recursive = TRUE)
```


```{r example}
library(camcorderplus)
library(ggplot2)
library(camcorder)

# Clean temp directory before use
unlink(file.path(tempdir(), "gg_history_export"), recursive = TRUE)

# Start recording
gg_record(device = "tiff", height = 10, width = 10, units = "cm")

# First plot
ggplot(mtcars, aes(x = wt, y = mpg, color = factor(cyl))) +
  geom_point(size = 3) +
  scale_color_viridis_d() +
  theme_minimal(base_size = 14) +
  ggtitle("MTCars: MPG vs Weight")

# Resize recording dimensions
gg_history_resize(height = 4, width = 7, units = "in")

# Second plot
ggplot(as.data.frame(Titanic), aes(x = Class, y = Freq, fill = Survived)) +
  geom_col(position = "dodge") +
  scale_fill_brewer(palette = "Paired") +
  theme_light(base_size = 16) +
  ggtitle("Titanic: Class vs Survival")

# Export all recorded plots
gg_history_export(create_export_folder = TRUE)
```

Images that were exported from the example above

```{r exported-images, echo = FALSE, results = "asis"}
img_dir <- file.path(tempdir(), "gg_history_export")
img_files <- list.files(img_dir, pattern = "\\.(png|jpe?g|bmp|tiff?)$", ignore.case = TRUE, full.names = TRUE)

# Create output directory where README.md will look for images
out_dir <- "man/figures/exported"
dir.create(out_dir, showWarnings = FALSE, recursive = TRUE)

# Copy and embed images using markdown
for (img in img_files) {
  new_path <- file.path(out_dir, basename(img))
  file.copy(img, new_path, overwrite = TRUE)
  cat(sprintf("![](%s)\n\n", new_path))
}
```
